### 2016-09-14 doc/publications/plos16/plos16.tex
brief start to feature importance

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Section 3: Feature Selection 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{CursedForest selects previously demonstrated cancer variants }
Feature selection can be useful for determining variables the contribute to the label or for perhaps selecting the n most important
variables for further analysis. Our Random Forest implementation allows the user to retrieve a subsection of features, ranked
by their importance. We demonstrate this feature on The Cancer Genome Atlas (TCGA) BRCA dataset. We build this model on
VCF files retrieved from the TCGA data portal. For the label, we use the cell type (i.e. tumor or normal).

In Table~\ref{table3}, we display the top 10 features, ranked by their Gini index in the Random Forest model.

\begin{table}[!ht]
%\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\centering
\caption{
{\bf Features from the TCGA BRCA dataset ranked by their importance.}}
\begin{tabular}{|l|l|l|l|l|l|l|}
\hline
{\bf Variant} & {\bf Gene} & {\bf Importance}\\ \thickhline
x:xxxx & cell2 row 1 & cell3 row 1\\ \hline
x:xxxx & cell2 row 2 & cell3 row 2\\ \hline
x:xxxx & cell2 row 3 & cell3 row 3\\ \hline
\end{tabular}
\begin{flushleft} Here the importance is the gini coefficient when building a model using the cell type as the label.
\end{flushleft}
\label{table3}
%\end{adjustwidth}
\end{table}
